---
title: "Survey Results"
author: "prepared by andrés castro araújo"
date: "Last Updated: `r format(Sys.Date())`"
output: 
  html_document: 
    theme: lumen
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.align = "center", comment = "", 
                      message = FALSE, warning = FALSE)

library(tidyverse)
source("prepareData.R")
source("helper-functions.R")

library(DT)
library(sf)
library(spData)

theme_set(theme_light(base_family = "Avenir Next Condensed"))
```

## Basics

-   Number of people who clicked on the survey:

    `r nrow(df)`

-   Number of respondents (people who finished the survey):

    `r nrow(df_clean)`

-   Number of respondents who clicked on the "I did not start a project at SICSS" option:

    `r sum(df_clean$type_1 == "I did not start a project at SICSS")`

-   Number of projects:

    `r sum(df_clean$type_1 != "I did not start a project at SICSS")`

-   Number of times the respondent has participated in a SICSS event:

    ```{r}
    df_clean$year |> map_dbl(length) |> table(dnn = "times")
    ```

-   Years:

    ```{r}
    df_clean$year |> unlist() |> table(dnn = "years")
    ```

-   SICSS Locations:

    ```{r}
    df_clean |> 
      unnest(site) |> 
      mutate(site = standardize_site(site)) |> 
      count(site, sort = TRUE) |> 
      DT::datatable()
    ```

-   Respondent Locations:

    Qualtrics only calculated this for the people who finished the survey. It did so automatically, I wasn't planning on collecting this data, but it looks good.

    ```{r}
    library(sf)
    library(spData)

    world_map <- spData::world %>% 
      sf::st_transform(crs = sf::st_crs(4326)) %>% 
      sf::st_transform("+proj=moll")

    map_points <- df_clean |> 
      sf::st_as_sf(
        coords = c("location_longitude", "location_latitude"), 
        crs = sf::st_crs(4326)
      ) %>% 
      sf::st_transform("+proj=moll")

    world_map %>% 
      ggplot() + 
      geom_sf(color = NA) +
      geom_sf(data = map_points, size = 1/2, alpha = 1/2, color = "steelblue") +
      coord_sf(crs = "+proj=moll") +
      theme_void()
    ```

## Projects

-   Type of project:

    ```{r}
    df_long |> 
      count(type, sort = TRUE) |> 
      DT::datatable()
    ```

-   Most common publications:

    ```{r}
    df_long |> 
      filter(type == "Publication") |> 
      count(publication, sort = TRUE) |> 
      DT::datatable()
    ```

-   Software

    ```{r}
    df_long |> 
      filter(type == "Software") |> 
      select(name, proj, website) |> 
      DT::datatable()
    ```

-   Community building

    ```{r}
    df_long |> 
      filter(type == "Community-building initiative") |> 
      select(name, proj, website) |> 
      DT::datatable()
    ```

-   Class or curriculum

    ```{r}
    df_long |> 
      filter(type == "Class or curriculum") |> 
      select(name, proj, website) |> 
      DT::datatable()
    ```

-   Other

    ```{r}
    df_long |> 
      filter(type == "Other") |> 
      select(name, proj, website) |> 
      DT::datatable()
    ```

## Open ended question

```{r}
df_oe <- df_clean |> 
  filter(!is.na(open_ended))

for (i in 1:nrow(df_oe)) {
  cat(df_oe$name[[i]], ":", "\n", str_trim(df_oe$open_ended[[i]]), "\n\n***\n\n")
}
```
